### 2016-08-28 paper.tex
Refer back to perf-covers fig as suggested by reviewer 3

Strut drag losses did not change much for the streamlined NACA 0021 struts in
the towed versus stationary configuration, which helps explain why overall rotor
drag coefficients remained of comparable magnitude even at low Reynolds number,
where $C_P$ was dramatically reduced, or even negative. For the cylindrical
struts, losses increased significantly when towed and operating in the mid range
of tip speed ratios.

>>>>

Strut drag losses did not change much for the streamlined NACA 0021 struts in
the towed versus stationary configuration, which helps explain why overall rotor
drag coefficients shown in Fig.~\ref{fig:perf-covers} remained of comparable
magnitude even at low Reynolds number, where $C_P$ was dramatically reduced, or
even negative. For the cylindrical struts, losses increased significantly when
towed and operating in the mid range of tip speed ratios.
